\scshape Topics in mechanism design

### 2025-12-07 ch2.tex
Add files via upload

`Who gets what?' is perhaps the most fundamental question in economics.
This chapter concerns research on that question.

The setting will be the same throughout: there are $I \geq 2$ agents, each of whom has a `type' $T_i$ that is randomly drawn from some set $\mathcal{T}_i$
according to a probability measure $\mu_i$
(defined on some $\sigma$-algebra).
Draws are independent across agents.%
	\footnote{This is important. When types are correlated, it is `typically' possible to incentivise agents to do essentially anything by offering them monetary bets on the other agents' types---see §\ref{sec:ch1:CremerMclean}.}
In most (but not all) models studied in this chapter, each agent $i$ privately knows her type $t_i \in \mathcal{T}_i$ from the outset.

@@

The standard IPV (independent private values) auction model fits this framework.
Here agent $i$'s type $t_i$ is her privately-known valuation of the good.
In an \emph{auction,} the agents take some actions (often called `bids'),
and as a function of these, the good is allocated and monetary payments are made by the agents.
Agents' payoffs are quasi-linear in money: $q_i t_i - p_i$, where $q_i \in [0,1]$ is $i$'s probability of getting the good, and $p_i \in \R$ is her payment.

@@

In all models we consider, agents have expected-utility preferences, so that their payoffs are linear in $q$; then if agents know their types when they take decisions, it only is the interim allocation that matters for their incentives.
Similarly, if the principal has an expected-utility objective that is additively separable across agents, then only the interim allocation matters to her.

@@

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\section{IPV auctions}
\label{sec:ch2:ipv}
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%

The \emph{IPV (independent private values) model} is the following.
Agents' types are drawn from $\mathcal{T}_i = [0,1]$, and are called \emph{valuations.}
(As before, they are statistically independent, and each agent learns only her own type.)
Payoffs are as in \cref{ch1}: if agent $i$ has type $t_i \in [0,1]$ and pays $p_i \in \R$, then her payoff is $t_i - p_i$ in case she gets the good, and $-p_i$ otherwise.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Equivalence of dominant-strategy and Bayes--Nash IC}
\label{sec::}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For example, an \emph{efficient} allocation is one that allocates the good always to one of those agents whose valuation is highest.
The first-price auction implements any efficient allocation as a Bayes--Nash equilibrium. (Convince/remind yourself.)
But consider the second-price auction: it also has an equilibrium implementing any efficient allocation, and in this equilibrium (in which each agent always bids her true value), agents' strategies are in fact weakly dominant.

@@

An allocation $q$ is \emph{Bayes--Nash (dominant-strategy) implementable}
iff there is a payment rule $p$ such that the direct mechanism $(q,p)$ is interim (dominant-strategy) IC.
Implementability is standardly characterised as follows:

@@

Applying the reasoning of \cref{ch1} agent-by-agent (in a similar way to how we reasoned agent-by-agent in the proof of \Cref{lemma:impl_mon} above)
yields that any Bayesian IC mechanism $(q,p)$ must satisfy the envelope formula
%
\begin{equation*}
	P_i(t_i) = P_i(0) + t_i Q_i(t_i) - \int_0^{t_i} Q_i
	\quad \text{for every $t_i \in [0,1]$ and $i$,}
\end{equation*}
%
that (interim) IR requires exactly that $P_i(0) \leq 0$ for each $i$,
and thus that revenue-maximising mechanisms have $P_i(0)=0$ for every $i$.
This reduces the revenue-maximisation problem to choosing an allocation $q$ to maximise
%
\begin{equation*}
	R(q) \coloneqq \sum_{i=1}^I R_i(Q_i) ,
	\quad \text{where} \quad
	R_i(Q_i)
	\coloneqq \E\left( T_i Q_i(T_i) - \int_0^{T_i} Q_i \right) ,
\end{equation*}
%
subject to the constraint that $Q_i$ be increasing for each agent $i$.

To rewrite the second term in $R_i(Q_i)$,
let $\phi_i(t_i) \coloneqq \int_0^{t_i} Q_i$;
then integrating by parts yields
%
\begin{multline*}
	\E\left( \int_0^{T_i} Q_i \right)
	= \int_0^1 \phi_i f_i
	= \left[ \phi_i F_i \right]_0^1
	- \int_0^1 \phi_i' F_i
	= \phi_i(1)
	- \int_0^1 Q_i F_i
	\\
	= \int_0^1 Q_i (1-F_i) .
\end{multline*}
%
Let $\boldsymbol{I} : [0,1] \to [0,1]$ denote the identity ($\boldsymbol{I}(t) \coloneqq t$ for every $t \in [0,1]$),
and let $V_i \coloneqq \boldsymbol{I} - \frac{1-F_i}{f_i}$;
this is called agent $i$'s \emph{virtual value.}
We have
%
\begin{equation*}
	R_i(Q_i)
	= \int_0^1 \boldsymbol{I} Q_i f_i
	- \int_0^1 \frac{1-F_i}{f_i} Q_i f_i 
	= \E\left[ V_i(T_i) Q_i(T_i) \right] .
\end{equation*}
%
The right-hand side is equal to
%
\begin{equation*}
	\E\Bigl[ V_i(T_i)
	\E\Bigl( q_i(t_i,\boldsymbol{T}_{-i})
	\Bigm| T_i=t_i \Bigr)
	\Bigr]
	= \E\bigl[ V_i(T_i) q_i(T_i,\boldsymbol{T}_{-i}) \bigr] 
\end{equation*}
%
by definition of $Q_i$ and the law of iterated expectations.
Thus expected revenue reads
%
\begin{align*}
	R(q)
	&= \E\left[ \sum_{i=1}^I V_i(T_i) q_i(\boldsymbol{T}) \right] .
\end{align*}

@@

\paragraph{The literature.}
Everything in this section is due to \textcite{Myerson1981}.
The `Myersonian approach' to the regular case has proved fruitful also in richer models in which more than just a single good is up for sale,
e.g. dynamic problems of selling goods over many periods \parencite{PavanSegalToikka2014}, problems of selling information \parencite{Yang2022}, and the problem of selling to a group \parencite{HaghpanahKuvalekarLipnowski2022}.
To understand what's really going on in the `Myersonian approach' (in particular, how to interpret the virtual valuations), I recommend \textcite[section~3.3]{Hartline2016}.

@@

In short, competition matters far more for revenue than the details of the auction design:
given the choice between setting an optimal reserve price
and having just \emph{one} extra bidder,
a revenue-maximising seller should always opt for the latter.
Insofar as the model assumptions are valid in a given practical situation (e.g. there is just one good, and values are private), this result provides rather sharp advice to sellers.

@@

	Now suppose that there is one additional agent.
	Consider the same second-price auction with reserve price $r$ and bidders $\{1,\dots,I\}$ (note that agent $I+1$ is not allowed to bid),
	except that whenever all bids are below the reserve price $r$,
	the good is awarded to agent $I+1$ instead of to nobody.
	This mechanism obviously raises expected revenue $R^\star$, and never keeps the good.
	Thus by \Cref{lemma:MyersonMustallocate}, the $(I+1)$-bidder second-price auction raises expected revenue at least $R^\star$.
	%
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Allocation with costly verification}
\label{sec:ch2:bdl14}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A principal can allocate an indivisible good to one of $I \geq 2$ agents.
Agents like the good and are expected-utility maximisers, so an agent's payoff is simply the probability with which she expects to receive the good.

@@

When costs $(c_i)_{i=1}^I$ differ across agents, favoured-agent mechanisms are defined as follows.
Agents report their `net types' $t_i-c_i$,
and there is a net-type threshold $\tau$.
If at least one agent's reported net type exceeds $\tau$,
then the agent with the highest-reported net type gets the good;
otherwise, the favoured agent gets the good.

@@

It is clearly without loss to consider only mechanisms in which,
if agent $i$ is checked and is found to have lied, then she certainly does not get the good.
That's because
if we take any mechanism in which truth-telling is a Bayes--Nash equilibrium
and modify it to never give the good to a verified liar,
then our new mechanism allocates the good just like the old one (since agents do not lie in equilibrium),
and truth-telling remains a best response for every agent
since lying is punished (even) more harshly in the new mechanism than in the old.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Equivalence of interim and ex-post IC}
\label{sec:ch2:bdl14:bic_epic}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Recall that an incentive-compatible mechanism $(q,e)$ is one in which truthful reporting is a Bayes--Nash equilibrium.
In other words, $(q,e)$ is IC exactly if its interim allocation and checking $(Q_i,E_i)_{i=1}^I$ satisfy
%
\begin{equation*}
	Q_i(t_i) \geq Q_i(t_i') - E_i(t_i')
	\quad \text{for every $i$ and all $t_i,t_i' \in \mathcal{T}_i$.}
\end{equation*}
%
The right-hand side here is the payoff of a type $t_i \neq t_i'$ from claiming to have type $t_i'$:
she gets allocated the good as if she really did have type $t_i'$ (viz. with probability $Q_i(t_i')$), \emph{except} if she gets checked (which happens with probability $E_i(t_i')$); in that case, she does not get the good.
If you don't find that explanation of the right-hand side convincing, then have a look at the addendum to this chapter (\cpageref{sec:ch2:bdl14:ic_deriv}), which contains a painstaking derivation of the right-hand side.

@@

\begin{lemma}
	%
	\label{lemma:bdl_epic}
	%
	$(q,e)$ is ex-post IC iff
	%
	\begin{equation*}
		e_i(\boldsymbol{t})
		\geq q_i(\boldsymbol{t})
		- \inf_{t_i' \in \mathcal{T}_i}
		q_i(t_i',\boldsymbol{t}_{-i})
		\quad \text{for every $i$ and all $\boldsymbol{t} \in \mathcal{T}_1 \times \cdots \times \mathcal{T}_I$,}
	\end{equation*}
	%
	and is interim IC iff its interim allocation and checking $(Q_i,E_i)_{i=1}^I$ satisfy
	%
	\begin{equation*}
		E_i(t_i)
		\geq Q_i(t_i) - \inf_{\mathcal{T}_i} Q_i
		\quad \text{for every $i$ and all $t_i \in \mathcal{T}_i$.}
	\end{equation*}
	%
\end{lemma}

\begin{proof}
	%
	Ex-post of $(q,e)$ requires precisely that
	for every agent $i$
	and profile $\boldsymbol{t} = (t_i,\boldsymbol{t}_{-i}) \in \mathcal{T}_i \times \mathcal{T}_{-i}$,
	%
	\begin{equation*}
		q_i(t_i',\boldsymbol{t}_{-i}) 
		\geq q_i(\boldsymbol{t}) - e_i(\boldsymbol{t}) 
		\quad \text{for every type $t_i' \in \mathcal{T}_i$.}
	\end{equation*}
	%
	This is equivalent to requiring
	for every agent $i$
	and profile $\boldsymbol{t}$
	that
	%
	\begin{equation*}
		\inf_{t_i' \in \mathcal{T}_i} q_i(t_i',\boldsymbol{t}_{-i}) 
		\geq q_i(\boldsymbol{t}) - e_i(\boldsymbol{t}) .
	\end{equation*}
	%
	Similarly for interim IC.
	%
\end{proof}

Ex-post IC appears much stronger than interim IC. And yet:

\begin{theorem}
	%
	\label{theorem:bdl_epic}
	%
	For any (interim) IC mechanism $(q,e)$,
	there is an ex-post IC mechanism that realises the same interim allocation and checking.
	%
\end{theorem}

@@

\begin{proof}
	%
	Let $(q,e)$ be interim IC,
	and write $(Q_i,E_i)_{i=1}^I$ for its interim allocation and checking.
	Wlog re-label each agent $i$'s types so that $Q_i$ is increasing.%
		\footnote{More formally, consider the alternative type spaces $\mathcal{T}_i' \coloneqq \{ Q_i(t_i) \}_{t_i \in \mathcal{T}_i}$.}
	Then by the \hyperref[theorem:manellivincent]{Manelli--Vincent theorem} (\cpageref{theorem:manellivincent}),
	there is an allocation $q'$ realising $(Q_i)_{i=1}^I$ such that $q_i'(\cdot,\boldsymbol{t}_{-i})$ is increasing (in the new order on the types) for every $i$ and $\boldsymbol{t}_{-i}$.
	Thus
	%
	\begin{equation*}
		\inf_{t_i' \in \mathcal{T}_i} \E
		\left[ q_i'(t_i',\boldsymbol{T}_{-i}) \right]
		= \E \left[ \inf_{t_i' \in \mathcal{T}_i} 
		q_i'(t_i',\boldsymbol{T}_{-i}) \right] .
	\end{equation*}

>>>>

This chapter concerns problems of allocating a single indivisible good among several competing claimants.

The setting will be the same throughout: there are $I \geq 2$ agents, who each have a `type' $T_i$ that is randomly drawn from some set $\mathcal{T}_i$
according to a probability measure $\mu_i$
(defined on some $\sigma$-algebra).
Draws are independent across agents.%
	\footnote{This is important. When types are correlated, it is `typically' possible to incentivise agents to do essentially anything by offering them monetary bets on the other agents' types---see §\ref{sec:ch1:CremerMclean}.}
In most (but not all) models studied in this chapter, each agent $i$ privately knows her type $t_i \in \mathcal{T}_i$ from the outset.

@@

The standard IPV (independent private valuations) auction model fits this framework.
Here agent $i$'s type $t_i$ is her privately-known valuation of the good.
In an \emph{auction,} the agents take some actions (often called `bids'),
and as a function of these, the good is allocated and monetary payments are made by the agents.
Agents' payoffs are quasi-linear in money: $q_i t_i - p_i$, where $q_i \in [0,1]$ is $i$'s probability of getting the good, and $p_i \in \R$ is her payment.

@@

In all models we consider, agents have expected-utility preferences, so that their payoffs are affine in $q$; then if agents know their types when they take decisions, it only is the interim allocation that matters for their incentives.
Similarly, if the principal has an expected-utility objective that is additively separable across agents, then only the interim allocation matters to her.

@@

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\section{Money (IPV auctions)}
\label{sec:ch2:ipv}
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%

The \emph{IPV (independent private valuations) model} is the following.
Agents' types are drawn from $\mathcal{T}_i = [0,1]$, and are called \emph{valuations.}
(As before, they are statistically independent, and each agent learns only her own type.)
Payoffs are as in \cref{ch1}: if agent $i$ has type $t_i \in [0,1]$ and pays $p_i \in \R$, then her payoff is $t_i - p_i$ in case she gets the good, and $-p_i$ otherwise.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Equivalence of dominant-strategy and Bayes--Nash IC}
\label{sec:ch2:manellivincent}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For example, an \emph{efficient} allocation is one that allocates the good always to one of those agents whose valuation is highest.
The first-price auction implements any efficient allocation as a Bayes--Nash equilibrium. (Convince/remind yourself.)
But consider the second-price auction: it also has an equilibrium implementing any efficient allocation, and in this equilibrium (in which each agent always bids her true valuation), agents' strategies are in fact weakly dominant.

@@

An allocation $q$ is \emph{Bayes--Nash (dominant-strategy) implementable}
iff there is a payment rule $p$ such that the direct mechanism $(q,p)$ is Bayes--Nash (dominant-strategy) IC.
Implementability is standardly characterised as follows:

@@

Applying the reasoning of \cref{ch1} agent-by-agent (in a similar way to how we reasoned agent-by-agent in the proof of \Cref{lemma:impl_mon} above)
yields that any Bayes--Nash IC mechanism $(q,p)$ must satisfy the envelope formula
%
\begin{equation*}
	P_i(t_i) = P_i(0) + t_i Q_i(t_i) - \int_0^{t_i} Q_i
	\quad \text{for every $t_i \in [0,1]$ and $i$,}
\end{equation*}
%
that (interim) IR requires exactly that $P_i(0) \leq 0$ for each $i$,
and thus that revenue-maximising mechanisms have $P_i(0)=0$ for every $i$.
This reduces the revenue-maximisation problem to choosing an allocation $q$ to maximise
%
\begin{equation*}
	R(q) \coloneqq \sum_{i=1}^I R_i(Q_i) ,
	\quad \text{where} \quad
	R_i(Q_i)
	\coloneqq \E\left( T_i Q_i(T_i) - \int_0^{T_i} Q_i \right) \quad \text{for each $i$,}
\end{equation*}
%
subject to the constraint that $Q_i$ be increasing for each agent $i$.

To rewrite the second term in $R_i(Q_i)$,
let $\phi_i(t_i) \coloneqq \int_0^{t_i} Q_i$ for each $t_i \in [0,1]$;
then integrating by parts yields
%
\begin{multline*}
	\E\left( \int_0^{T_i} Q_i \right)
	= \int_0^1 \phi_i f_i
	= \left[ \phi_i F_i \right]_0^1
	- \int_0^1 \phi_i' F_i
	= \phi_i(1)
	- \int_0^1 Q_i F_i
	\\
	= \int_0^1 Q_i (1-F_i) .
\end{multline*}
%
Let $\boldsymbol{I} : [0,1] \to [0,1]$ denote the identity ($\boldsymbol{I}(t) \coloneqq t$ for every $t \in [0,1]$),
and let $V_i \coloneqq \boldsymbol{I} - \frac{1-F_i}{f_i}$;
this is called agent $i$'s \emph{virtual valuation.}
We have
%
\begin{equation*}
	R_i(Q_i)
	= \int_0^1 \boldsymbol{I} Q_i f_i
	- \int_0^1 \frac{1-F_i}{f_i} Q_i f_i 
	= \E\left[ V_i(T_i) Q_i(T_i) \right] .
\end{equation*}
%
The right-hand side is equal to
%
\begin{equation*}
	\E\Bigl[ V_i(T_i)
	\E\Bigl( q_i(t_i,\boldsymbol{T}_{-i})
	\Bigm| T_i=t_i \Bigr)
	\Bigr]
	= \E\bigl[ V_i(T_i) q_i(T_i,\boldsymbol{T}_{-i}) \bigr] 
\end{equation*}
%
by definition of $Q_i$ and the law of iterated expectations.
Thus expected revenue reads
%
\begin{equation*}
	R(q)
	= \E\left[ \sum_{i=1}^I V_i(T_i) q_i(\boldsymbol{T}) \right] .
\end{equation*}

@@

\paragraph{The literature.}
Everything in this section is due to \textcite{Myerson1981}.
The `Myersonian approach' to the regular case has proved fruitful also in richer models in which more than just a single good is up for sale,
e.g. dynamic problems of selling goods over many periods \parencite{PavanSegalToikka2014}, problems of selling information \parencite{Yang2022}, and the problem of selling to a group \parencite{HaghpanahKuvalekarLipnowski2022}.
To understand what's really going on in the `Myersonian approach' (in particular, how to interpret the virtual valuations), I recommend \textcite[section~3.3]{Hartline2016} (which is ultimately based on \cite{BulowRoberts1989}).

@@

In short, competition matters far more for revenue than the details of the auction design:
given the choice between setting an optimal reserve price
and having just \emph{one} extra bidder,
a revenue-maximising seller should always opt for the latter.
Insofar as the model assumptions are valid in a given practical situation (e.g. there is just one good, and valuations are private), this result provides rather sharp advice to sellers.

@@

	Now suppose that there is one additional agent.
	Consider the same second-price auction with reserve price $r$ and bidders $\{1,\dots,I\}$ (note that agent $I+1$ is not allowed to bid),
	except that whenever all bids are below the reserve price $r$,
	the good is awarded (for free) to agent $I+1$ instead of to nobody.
	This mechanism obviously raises expected revenue $R^\star$, and never keeps the good.
	Thus by \Cref{lemma:MyersonMustallocate}, the $(I+1)$-bidder second-price auction raises expected revenue at least $R^\star$.
	%
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\section{Wasteful effort}
\label{sec:ch2:effort}
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%

Consider a principal who allocates an indivisible good among $I \geq 2$ agents. Monetary transfers are unavailable, but the principal has access to a money-like incentive instrument called \emph{effort.}

Concretely, the model is exactly the smooth IPV model from the previous section, except that instead of making a payment $p_i \in \R$, each agent \emph{observably} exerts some effort $e_i \in \R_+$ at a cost $c_i(e_i) \in \R_+$, where $c_i : \R_+ \to \R_+$ is strictly increasing. We assume that $c_i$ is onto $\R_+$; equivalently, that it is continuous and unbounded above with $c_i(0)=0$. The agent's type $t_i \in [0,1]$ can still be interpreted as her willingness to pay for the good, but it is now denominated in units of cost rather than in dollars. (Cost could be denominated in dollars, but it need not be.)

The principal's objective can no longer be revenue, since there is no money in this economy. We shall instead assume that the principal has the agents' best interests at heart, seeking to maximise utilitarian welfare, i.e. the sum of agents' payoffs. This entails an assumption that the principal does not benefit from effort, so that effort is socially wasteful.

`Effort' in this model is precisely a costly signal à la \textcite{Spence1973}; his single-crossing property is (obviously) satisfied, as higher types are by definition exactly those who are more willing to exert effort to obtain the good. An important example of wasteful effort is queuing; many goods (e.g. social housing) are allocated in this way. Another example is when effort \emph{is} money (and $c_i(p_i)=p_i$ for each $p_i \in \R_+$); this is the case in which agents can `burn' money (i.e. waste it), giving the principal no benefit but signalling willingness to pay for the good.

We also that each agent $i$'s cost function $c_i$ is known by the principal. This is potentially a strong assumption. We can accommodate a degree of private information about costs by assuming that $c_i = \theta_i C_i$, where $\theta_i \in \R_{++}$ is privately known by agent $i$ and $C_i : \R_+ \to \R_+$ is commonly known; then the agent's (renormalised) payoff is $(t_i/\theta_i) q_i - C_i(e_i)$, so it is as if the agent has commonly known cost function $C_i$ and private type $t_i/\theta_i$.

A \emph{mechanism} is now a pair $(q,e)$, where $q$ is an allocation (i.e. a map $q : [0,1]^I \to [0,1]^I$ such that $\sum_{i=1}^I q_i \leq 1$) and $e$ is a map $[0,1]^I \to \R_+^I$. It is more convenient to work with a reparametrisation whereby a mechanism specifies the \emph{cost} of effort $p_i = c_i(e_i) \in \R_+$ rather than effort itself; this change of variables is permissible since $c_i$ is bijective (one-to-one and onto). Concretely, a mechanism is then a pair $(q,p)$, where $q$ is an allocation and $p$ is a \emph{non-negative} `payment' rule, i.e. a map $p : [0,1]^I \to \R^I$ satisfying the constraint $p \geq 0$. The principal's problem is to maximise
%
\begin{equation*}
	\E\left( \sum_{i=1}^I \left[ T_i q(\boldsymbol{T}) - p(\boldsymbol{T}) \right] \right)
\end{equation*}
%
among all Bayes--Nash IC mechanisms $(q,p)$. (We have neglected participation; this will not matter below.)

Following the argument for \Cref{lemma:impl_mon} in \cref{sec:ch2:manellivincent} above, a mechanism $(q,p)$ that realises interim allocation $(Q_i)_{i=1}^I$ and interim `payment' rule $(P_i)_{i=1}^I$ is Bayes--Nash IC if and only if for each agent $i$, $Q_i$ is increasing and the envelope formula
%
\begin{equation*}
	t_i Q_i(t_i) - P_i(t_i) 
	= - P_i(0)
	+ \int_0^{t_i} Q_i
	\quad \text{for every $t_i \in [0,1]$}
\end{equation*}
%
is satisfied. It is optimal to set $P_i(0)=0$ for every agent $i$ (why?). The principal's problem then reduces to choosing an allocation $q$ to maximise
%
\begin{equation*}
	W(q) \coloneqq \sum_{i=1}^I W_i(Q_i) ,
	\quad \text{where} \quad
	W_i(Q_i)
	\coloneqq \E\left( \int_0^{T_i} Q_i \right) \quad \text{for each $i$,}
\end{equation*}
%
subject to the constraint that $Q_i$ be increasing for each agent $i$. A small variation on the integration-by-parts argument in \cref{sec:ch2:optimal_auctions} above shows that
%
\begin{equation*}
	W(q)
	= \E\left[ \sum_{i=1}^I S_i(T_i) Q_i(T_i) \right]
	= \E\left[ \sum_{i=1}^I S_i(T_i) q_i(\boldsymbol{T}) \right] ,
\end{equation*}
%
where $S_i \coloneqq (1-F_i)/f_i$ for each agent $i$.

The object $f_i / (1-F_i) = 1/S_i$ is called the \emph{hazard rate} of the CDF $F_i$. In the IPV auctions context, it is frequently assumed that each agent $i$'s hazard rate is increasing; this is a sufficient condition for regularity, i.e. for the virtual valuation $V_i = \boldsymbol{I} - S_i$ to be increasing for each agent $i$.

\begin{proposition}
	%
	\label{proposition:condorelli}
	%
	If the hazard rate $f_i/(1-F_i)$ is increasing for each agent $i$, then it is optimal give the good away, with no effort exerted.
	%
\end{proposition}

In other words, there is an optimal mechanism $(q,p)$ such that $q$ is constant and $p=0$.

The benefit of screening using effort is that it leads higher-type agents to tend to receive the good. The cost is that effort is socially wasteful. \Cref{proposition:condorelli} says that the cost always outweighs the benefit, whatever the type distributions $(F_i)_{i=1}^I$, so long as they have increasing hazard rates.

\begin{proof}
	%
	Let $(q,p)$ be an arbitrary Bayes--Nash IC mechanism; we will find another Bayes--Nash IC mechanism which is weakly better. In particular, let $k_i \coloneqq \E(q_i(\boldsymbol{T}))$ for each agent $i$, define an allocation $q'$ by $q_i' \coloneqq k_i$ for each agent $i$, and consider the mechanism $(q',0)$. This mechanism simply randomly assigns the good, with the good going to agent $i$ with probability $k_i$, and with no effort being exerted. It is obviously Bayes--Nash (indeed, dominant-strategy) IC. And it is weakly better since for each agent $i$, $S_i$ is decreasing and $Q_i$ is increasing, so the random variables $X_i \coloneqq S_i(T_i)$ and $Y_i \coloneqq Q_i(T_i)$ satisfy $\Cov(X_i,Y_i) \leq 0$, and thus
	%
	\begin{equation*}
		\E\left[ S_i(T_i) Q_i(T_i) \right]
		\leq \E\left[ S_i(T_i) \right]
		\E\left[ Q_i(T_i) \right]
		= \E\left[ S_i(T_i) k_i \right]
		= \E\left[ S_i(T_i) Q_i'(T_i) \right] ,
	\end{equation*}
	%
	whence $W(q) \leq W(q')$.
	%
\end{proof}

\begin{exercise}
	%
	\label{exercise:condorelli_foc}
	%
	In \Cref{proposition:condorelli}, \emph{which} agent optimally receives the good? Under what circumstances is it optimal to allocate the good by a fair lottery?
	%
\end{exercise}

If the hazard rate $f_i/(1-F_i)$ is instead \emph{decreasing,} then the argument from \cref{sec:ch2:optimal_auctions} implies that it is optimal to assign the good to whichever agent $i$ has the lowest hazard rate $f_i(t_i)/(1-F_i(t_i))$. In the symmetric case, when $F_i=F$ for every agent $i$ (and $f/(1-F)$ is decreasing), this means that the agent with the highest type receives the good.

This `highest type gets the good' allocation may be paired with any interim `payment' rule such that type $0$ expends no effort and the envelope formula is satisfied. Three different such `payment' rules are those arising from the first-price auction, the second-price auction, and the all-pay auction. Each of these can implemented in practice by first asking agents to make boasts (or `bids', i.e. cheap-talk reports) about how much effort they are willing to carry out, and then asking agents to actually exert effort in accordance with the auction format, awarding the good to the most boastful agent (assuming she exerted effort as promised---recall that this is observable by assumption). In particular, (only) the most boastful agent is asked to make good her boast in the first-price auction, all agents are asked to make good their boasts in the all-pay auction, while in the second-price auction, (only) the most boastful agent is asked to exert effort, but only enough to match the second-most boastful agent's boast.

The all-pay auction can be implemented without communication (boasts), by simply asking all agents to exert effort, and then awarding the good to whoever exerted the most. When effort is time spent queuing, the first-price auction can be implemented as follows: announce a time, promise to give the good to whoever is at the front of the queue at that time, and let agents join he queue as early as they like (then the agent who shows up first will queue until the good is awarded, and no other agents will join the queue).%
	\footnote{Thanks to James Lester for suggesting this implementation.}

\paragraph{The literature.}
The ideas and results in this section were independently discovered by \textcite{HartlineRoughgarden2008,Yoon2011,Condorelli2012,ChakravartyKaplan2013}, and have been getting popular following the success of \textcite{DworczakKominersAkbarpour2021}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Costly, noiseless monitoring}
\label{sec:ch2:bdl14}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A principal can allocate an indivisible good to one of $I \geq 2$ agents.
Agents like the good and are e
xpected-utility maximisers, so an agent's payoff is simply the probability with which she expects to receive the good.

@@

When costs $(c_i)_{i=1}^I$ differ across agents, favoured-agent mechanisms are defined as follows.
Agents report their `net types' $t_i-c_i$,
and there is a net-type threshold $\tau$.
If at least one agent's reported net type exceeds $\tau$,
then the agent with the highest-reported net type is checked, and provided her report was true, she gets the good;
otherwise, the favoured agent gets the good.

@@

It is clearly without loss to consider only mechanisms in which,
if agent $i$ is checked and is found to have lied, then she certainly does not get the good.
That's because
if we take any mechanism in which truth-telling is a Bayes--Nash equilibrium
and modify it to never give the good to a proven liar,
then our new mechanism allocates the good just like the old one (since agents do not lie in equilibrium),
and truth-telling remains a best response for every agent
since lying is punished (even) more harshly in the new mechanism than in the old.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Equivalence of Bayes--Nash and ex-post IC}
\label{sec:ch2:bdl14:bic_epic}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Recall that a Bayes--Nash incentive-compatible mechanism $(q,e)$ is one in which truthful reporting is a Bayes--Nash equilibrium.
In other words, $(q,e)$ is Bayes--Nash IC exactly if its interim allocation and checking $(Q_i,E_i)_{i=1}^I$ satisfy
%
\begin{equation*}
	Q_i(t_i) \geq Q_i(t_i') - E_i(t_i')
	\quad \text{for every $i$ and all $t_i,t_i' \in \mathcal{T}_i$.}
\end{equation*}
%
The right-hand side here is the payoff of a type $t_i \neq t_i'$ from claiming to have type $t_i'$:
she gets allocated the good as if she really did have type $t_i'$ (viz. with probability $Q_i(t_i')$), \emph{except} if she gets checked (which happens with probability $E_i(t_i')$); in that case, she does not get the good.
If you don't find that explanation of the right-hand side convincing, then have a look at the addendum to this chapter (\cpageref{sec:ch2:bdl14:ic_deriv}), which contains a painstaking derivation of the right-hand side.

@@

\begin{lemma}
	%
	\label{lemma:bdl_epic}
	%
	$(q,e)$ is ex-post IC iff
	%
	\begin{equation*}
		e_i(\boldsymbol{t})
		\geq q_i(\boldsymbol{t})
		- \inf_{t_i' \in \mathcal{T}_i}
		q_i(t_i',\boldsymbol{t}_{-i})
		\quad \text{for every $i$ and all $\boldsymbol{t} \in \mathcal{T}_1 \times \cdots \times \mathcal{T}_I$,}
	\end{equation*}
	%
	and is Bayes--Nash IC iff its interim allocation and checking $(Q_i,E_i)_{i=1}^I$ satisfy
	%
	\begin{equation*}
		E_i(t_i)
		\geq Q_i(t_i) - \inf_{\mathcal{T}_i} Q_i
		\quad \text{for every $i$ and all $t_i \in \mathcal{T}_i$.}
	\end{equation*}
	%
\end{lemma}

\begin{proof}
	%
	Ex-post of $(q,e)$ requires precisely that
	for every agent $i$
	and profile $\boldsymbol{t} = (t_i,\boldsymbol{t}_{-i}) \in \mathcal{T}_i \times \mathcal{T}_{-i}$,
	%
	\begin{equation*}
		q_i(t_i',\boldsymbol{t}_{-i}) 
		\geq q_i(\boldsymbol{t}) - e_i(\boldsymbol{t}) 
		\quad \text{for every type $t_i' \in \mathcal{T}_i$.}
	\end{equation*}
	%
	This is equivalent to requiring
	for every agent $i$
	and profile $\boldsymbol{t}$
	that
	%
	\begin{equation*}
		\inf_{t_i' \in \mathcal{T}_i} q_i(t_i',\boldsymbol{t}_{-i}) 
		\geq q_i(\boldsymbol{t}) - e_i(\boldsymbol{t}) .
	\end{equation*}
	%
	Similarly for Bayes--Nash IC.
	%
\end{proof}

Ex-post IC appears much stronger than Bayes--Nash IC. And yet:

\begin{theorem}
	%
	\label{theorem:bdl_epic}
	%
	For any Bayes--Nash IC mechanism $(q,e)$,
	there is an ex-post IC mechanism that realises the same interim allocation and checking.
	%
\end{theorem}

@@

\begin{proof}
	%
	Let $(q,e)$ be Bayes--Nash IC,
	and write $(Q_i,E_i)_{i=1}^I$ for its interim allocation and checking.
	Wlog re-label each agent $i$'s types so that $Q_i$ is increasing.%
		\footnote{More formally, consider the alternative type spaces $\mathcal{T}_i' \coloneqq \{ Q_i(t_i) \}_{t_i \in \mathcal{T}_i}$.}
	Then by the \hyperref[theorem:manellivincent]{Manelli--Vincent theorem} (\cpageref{theorem:manellivincent}),
	there is an allocation $q'$ realising $(Q_i)_{i=1}^I$ such that $q_i'(\cdot,\boldsymbol{t}_{-i})$ is increasing (in the new order on the types) for every $i$ and $\boldsymbol{t}_{-i}$.
	Thus
	%
	\begin{equation*}
		\inf_{t_i' \in \mathcal{T}_i} \E
		\left[ q_i'(t_i',\boldsymbol{T}_{-i}) \right]
		= \E \left[ \inf_{t_i' \in \mathcal{T}_i} 
		q_i'(t_i',\boldsymbol{T}_{-i}) \right] .
	\end{equation*}
